Lattice Boltzmann simulations of magnetically responsive\\ ellipsoidal particle stabilized emulsions

### 2025-03-10 chapters/paper2.tex
Changes 1. Added more figures for introduction and literature review 2. Completed introduction and lit review for draft 1 3. Added figures for Aim 3 section
Changes 1. Refined text in most sections 2. Resized figures for consistency of figure size 3. Removed shear banding analysis and added how shear stress is calculated

This work investigates the structural response of bijels stabilized by anisotropic magnetic particles. Using a Lattice Boltzmann Method 
coupled with Molecular Dynamics, we simulate a binary fluid system where ellipsoidal particles, modeled as magnetic dipoles along their 
symmetry axis, stabilize bijel templates. Simulations without an applied field reveal anisotropic bijel formation, with microstructure 
evolution dependent on particle reordering at the interface, quantified using the six-fold Steinhardt order parameter \(\langle Q_6 \rangle\).

@@

In Figure \ref{fig:particle_viz-field_on}, we see the effect of the
application of the magnetic field on the monolayer. The initial
configuration of particles at the monolayer show that the orientations
are random and that the particles tend to lie flat on the interface.
However, upon application of the magnetic field the particles orient to
the field direction. The effect that Gunther. et al.~observed for bijels
stabilized with anisotropic particles can also be observed in these
snapshots as the particles can be observed to have more local order in
the final state than in the initial state with no applied field. We
observe that for bijels stabilized by prolate ellipsoids, we see the
adoption of more regular arrangements of the colloids on the interface.
We investigate the effect of local particle ordering next. Past work by
Bresme and Faraudo and Davies investigating the reorientation of
particles at interfaces under magnetic fields have shown that a critical
magnetic field exists, above which the particle orients to the field and
below which the particle orientation is a function of the capillary
force and magnetic field derived force. \cite{davies_interface_2014}
\cite{bresme_orientational_2007} Particle adsorption into the interface
with microparticles have also been shown to be irreversible due to the
high adsorption energy. Upon particle reorientation, the microstructure
change can be driven solely through particle unjamming and re-jamming,
or it can be driven through the particles dragging the interface during
this process. The mechanism of unjamming and re-jamming can be
investigated using the average interfacial angle, $\langle \psi \rangle$
and the local ordering of the particles characterized with 
$\langle Q_6 \rangle$ Past work has identified that local crystallization 
of colloidal crystals takes place at \(\langle Q_6 \rangle = 0.38\). 
\cite{toxvaerd_role_2020}

\begin{figure} 
\centering 
\includegraphics[scale=0.5]{../figures/results/paper2/interface_angle-nint-field_on.png} 
\caption{Plots of the interface angle $(\langle \psi \rangle)$ and six fold Steinhardt order parameter $(\langle Q_6 \rangle)$ on the left and right respectively, versus time for bijels stabilized with oblate and prolate ellipsoids on the top and bottom rows respectively. We demonstrate that upon application of a magnetic field, the behavior of $(\langle \psi \rangle)$ and $(\langle Q_6 \rangle)$ differ significantly between oblate and prolate ellipsoids indicating that the dynamics for both particle morphologies differ. We also observe magnetic field dependence in each property for both particle types, suggesting that these changes are driven primarily through the change in the applied field strength.} 
\label{fig:interface_angle-nint-field_on} 
\end{figure}

@@

When analyzing \(\langle \psi \rangle\) for bijels stabilized by prolate
particles, this behavior can also be observed. \(\langle \psi \rangle\)
begins at \(80 ^{circ}\). The difference in the initial
\(\langle \psi \rangle\) compared to oblate particles is due to the
direction of the axis of symmetry. In prolate particles, the axis of
symmetry lies parallel with the interface and \(\langle \psi \rangle\)
measures the angle between the interface normal and the orientation of
the axis of symmetry. We see \(\langle \psi \rangle\) decrease slightly,
before plateauing and slowly increasing again. The rate of decrease in
\(\langle \psi \rangle\) is field dependent, although given the small
decrease in \(\langle \psi \rangle\) it is unclear if the final value of
this parameter is field dependent for bijels stabilized with prolate
particles. The changes in \(\langle \psi \rangle\) for bijels stabilized
with prolate particles are small compared to bijels stabilized with
oblate particles. We believe this is due to local particle effects at
the interface. We probe this by identifying the local particle ordering
at the interface characterized by \(\langle Q_6 \rangle\).

We see that for oblate particles, \(\langle Q_6 \rangle\) sees a
decrease from its initial value. However the dynamics are controlled by
the applied magnetic field strength. We split the phases of dynamics
into three sections, similar to \(\langle \psi \rangle\) with the first
section seeing a decrease in \(\langle Q_6 \rangle\) upon application of
the magnetic field, followed by a plateau and finally a gradual increase
before jamming takes place. These results indicate that the ordering of
the particles is reduced by the applied magnetic field, before a
restoration of some of the pre-existing order. The final values of
\(\langle Q_6 \rangle\) are magnetic field dependent, with a stronger
magnetic field having a lower final \(\langle Q_6 \rangle\) value
indicating that either the ordering of particles influence the angle at
the interface or vice versa. We observe that for bijels stabilized by
oblate particles, the interface ordering of the particles increases as a
function of the applied field strength. We also observe from plotting
\(\langle Q_6 \rangle\) that application of a magnetic field creates a
local crystallization of the colloid monolayer characterized as
\(\langle Q_6 \rangle > 0.38\). \cite{toxvaerd_role_2020}

Figure \ref{fig:domain_size-field_on}, we observed a gap between the
growth of the nematic order parameter and an increase in the domain
size. To probe why this occurs, we recast \(\langle \psi \rangle\),
\(\langle Q_6 \rangle\) and \(S\) in terms of the physical phenomena
they represent. The nematic order parameter represents the ordering of
particles to an average direction, which in the case of the application
of a magnetic field, is the field direction. Therefore, a timescale
reliant on the nematic order parameter would represent a timescale of
response rate limited to the response to the magnetic field, which
indicates a particle-field orientation dependence. We name this
timescale \(\tau_S\). When applying a field to a bijel system with a
randomly oriented particle monolayer, the most significant transition
point is the isotropic to nematic transition or when \(S \geq 0.3\). We
define \(\tau_S\) for this section of the analysis by identifying when
\(S \geq 0.3\).

We can also do the same for \(\langle \psi \rangle\) and
\(\langle Q_6 \rangle\). A timescale derived from
\(\langle \psi \rangle\) named \(\tau_{\langle \psi \rangle}\)
represents the capillary timescale between the interface and the
particle. Given the shape of the plot, we assign the
\(\tau_{\langle \psi \rangle}\) to be the time when the first minimum of
\(\langle \psi \rangle\) is observed for prolate particles and the first
maximum for oblate particles. A timescale derived from
\(\langle Q_6 \rangle\), named \(\tau_{\langle Q_6 \rangle}\) is also
calculated which represents a timescale of local particle rearrangement.
We define \(\tau_{\langle Q_6 \rangle}\) as the time when
\(\langle Q_6 \rangle \geq 0.38\) for prolate particles and the global
minimum of \(\tau_{\langle Q_6 \rangle}\) for the oblate particles. We
omit \(\bar{B} = 0\) as previous results have identified the domain size
changes observed there. We then plot the average domain size \(L\)
against time rescaled with these three timescales in Figure
\ref{fig:domain_size-field_on-scaled}.

\begin{figure} 
\centering 
\includegraphics[scale=0.4]{../figures/results/paper2/domain_size-field_on-scaled.png} 
\caption{Plots of domain size with different timescales. The top and bottom row represent the average domain size for bijels stabilized with oblate and prolate particles respectively. The figures on the left plots the domain size against time rescaled with the nematic to isotropic transition time, $\tau_S$. The figures in the middle plot the domain size against time rescaled with the interfacial capillary timescale, $\tau_{\langle \psi \rangle}$. The figures on the right plot the domain size against time rescaled with the particle rearrangement timescale, $\tau_{\langle Q_6 \rangle}$. We show that the controlling timescale when applying a magnetic field onto bijels with disordered particles is the latter timescale, indicating that the dominating effect is steric hindrance of the particles during rearrangment at the interface.} 
\label{fig:domain_size-field_on-scaled} 
\end{figure}

@@

The right plot demonstrates the domain size change after rescaling time
with \(\tau_{\langle Q_6 \rangle}\) where we see good collapse between
all plots while the domain size transition also begins at
\(\frac{t}{\tau_{\langle Q_6 \rangle}} = 1\). The latter point
demonstrates that the dynamics for the structural response of randomly
oriented particles are controlled by the local particle rearrangement at
the interface rather than the orientation of the particle to the
magnetic field.We see that before \(\tau_{\langle Q_6 \rangle} = 1\),
\(\bar{B} = 0.2\) for the oblate particles does not collapse onto the
other plots, indicating that the dynamics before that point are
controlled by another phenomena.

@@

In Figure \ref{fig:particle_viz-field_up}, we see the effect of the
application of the magnetic field on the monolayer. The initial
configuration of particles at the monolayer show that even at initial
configuration of run \(\bar{B}: 0.2 \rightarrow 1\), most particles are
oriented towards the field. Upon increasing the field strength to
\(\bar{B} = 1\), all particles shown can be seen to be ordered to the
field, matching the results for the nematic order parameter shown in
Figure \ref{fig:domain_size-field_up}. We also observe the alignment of
the long axis of the particles to the magnetic field, demonstrating the
origin of the microstructure anisotropy. To understand how the particle
reorientation at the interface causes microstructure reorientation we
quantify the average interface angle, \(\langle \psi \rangle\) and the
local interface order of the material, \(\langle Q_6 \rangle\) in Figure
\ref{fig:interface_angle-nint-field_up}.

@@

From Figure \ref{fig:interface_angle-nint-field_up}, we identify that
prolate and oblate particles respond differently at the interface. We
show that there are three time evolution trends for
\(\langle \psi \rangle\) and \(\langle Q_6 \rangle\) for both oblate and
prolate particles despite the differences in the initial state of the
particles. In oblate particles \(\langle \psi \rangle\) begins closer to
\(0 ^{\circ}\) as the axis of symmetry lies close to the interface
normal. We see that for bijels experiencing a field strength history of
\(\bar{B}: 0 \rightarrow 1\) and \(\bar{B}: 0.2 \rightarrow 1\),
\(\langle \psi \rangle\) increases, plateaus and increases again before
plateauing again. This is indicative of particles tilting at the
interface, before interfacial capillary interactions ``pause'' particle
reorientation before the applied magnetic field begins to cause
particles to tilt out of the interface. We see similar trends for bijels
stabilized by prolate particles. \(\langle \psi \rangle\) begins near
\(80 ^{\circ}\). We see a decrease before reorientation ceases, and
finally \(\langle \psi \rangle\) increases again.

When looking at \(\langle Q_6 \rangle\) for \(\bar{B}: 0 \rightarrow 1\)
and \(\bar{B}: 0.2 \rightarrow 1\) for oblate particles, we see that the
trends are similar with an initial decrease, followed by a plateau and
increase over time before plateauing again. \(\langle Q_6 \rangle\)
generally decreases with a large decrease observed for
\(\bar{B}: 0 \rightarrow 1\) from an initial hexagonally packed system
to a structure that is locally ordered but not close packed. For prolate
particles, we see an increase in \(\langle Q_6 \rangle\) with a plateau
occurring in both systems around 5000 timesteps. The significance of
this time is unknown for \(\bar{B}: 0.2 \rightarrow 1\) but for
\(\bar{B}: 1 \rightarrow 1\), this is approximately the local
crystallization point when \(\langle Q_6 \rangle \geq 0.38\).

For oblate particles, we can conclude that structural response dynamics
arise from particle tilting on the interface identified as the large
difference between the initial and final \(\langle \psi \rangle\) with
an associated decrease in the interface coverage, initiating domain
coarsening. We see that this interfacial tilting causes a loss in the
close packing of oblate particles at the interface. For prolate
particles, we observe a small degree of particle tilting as can be seen
from \(\langle \psi \rangle\), although the dynamics are primarily
driven by the change in \(\langle Q_6 \rangle\), indicated as a slight
dip and plateau before the particles begin reordering and packing more
tightly, decreasing the interfacial area. Larger domain size response is
observed for the prolate particles as the interfacial area change from
particle tilting at the interface is larger than that of particles close
packing at the interface.

For both particle morphologies we analyze the response of bijels with a
field history of \(\bar{B}: 0.5 \rightarrow 1\) and
\(\bar{B}: 1 \rightarrow 1\). We see a decrease in
\(\langle Q_6 \rangle\) for bijels stabilized with oblate particles with
field application of \(\bar{B}: 0.5 \rightarrow 1\) compared to an
increase for \(\bar{B}: 1 \rightarrow 1\). This behavior arises from the
slight increase in the nematic order for particles in bijels
experiencing the \(\bar{B}: 0.5 \rightarrow 1\) field application
history. The \(\langle \psi \rangle\) results indicate that the
particles rearrange over time to lie flatter on the interface. For
bijels stabilized with prolate particles, we characterize a difference
in behavior between \(\bar{B}: 0.5 \rightarrow 1\) and
\(\bar{B}: 1 \rightarrow 1\). For the \(\bar{B}: 0.5 \rightarrow 1\)
case, we see a slight increase in \(\langle \psi \rangle\) before a
decrease and increase compared to the \(\bar{B}: 1 \rightarrow 1\) case
where we characterize a slight decrease over time. We also characterize
a slight decrease in \(\langle Q_6 \rangle\) over time for the
\(\bar{B}: 1 \rightarrow 1\) case while characterizing a larger decrease
for the \(\bar{B}: 0.5 \rightarrow 1\) case. Similar to the oblate
particles, these results originate from the slight increase in the
nematic order for bijels experiencing the \(\bar{B}: 0.5 \rightarrow 1\)
field history.

@@

In Figure \ref{fig:domain_size_aniso-field_down}, we see that there are
small \(\Delta \bar{B}\) dependent changes in the anisotropic domain
size and tortuosity for both particle morphologies. However, there are
no clear trends that can be developed from these plots, suggesting that
the changes are overall isotropic and any differences observed arise
from the arrangement of particles. This suggests that the response of
the material to the removal of a magnetic field is isotropic and only
dependent upon the capillary interactions with the particle monolayer.
We showed earlier that the application of magnetic fields change the
local state of the particles at the interface. However the results shown
thus far demonstrate that that these changes do not seem to affect the
coarsening of the bijel once stimuli is removed. To investigate why this
is the case, we plot \(\langle \psi \rangle\) and
\(\langle Q_6 \rangle\) for bijels stabilized with ellipsoidal particles
below.

@@

In Figure \ref{fig:interface_angle-field_down}, we plot
\(\langle \psi \rangle\) and \(\langle Q_6 \rangle\) in the left and
right columns respectively. While there are minor differences to the
time when \(\langle \psi \rangle\) and \(\langle Q_6 \rangle\) increase
and decrease respectively for bijels stabilized by oblate particles the
trends are identical. This suggests that the differences in particle
angle, local ordering and nematic order only change when coarsening will
take place without affecting its dynamics.

@@

Looking at \(\langle Q_6 \rangle\), we see that all simulations see a
decrease over time. We see that contrary to previous trends, the
\(\bar{B}: 1\rightarrow 0\) simulation has a smaller change in
\(\langle Q_6 \rangle\) than \(\bar{B}: 0.5\rightarrow 0\) although this
difference is also a result of the initial particle orientation and
position, rather than a defining feature of a broader trend. We see that
the \(\bar{B}: 0.5\rightarrow 0\) case is near the
\(Q_6^{HCP} \approx 0.485\) boundary, suggesting it is most susceptible
to lose short range order upon removal of the magnetic field that
enforces it, resulting in the large decrease in \(\langle Q_6 \rangle\)
observed.

>>>>

This work investigates the structural response of bijels stabilized by anisotropic magnetic particles. Using a Lattice Boltzmann Method 
coupled with Molecular Dynamics, we simulate a binary fluid system where ellipsoidal particles, modeled as magnetic dipoles along their 
symmetry axis, stabilize bijel templates. Simulations without an applied field reveal anisotropic bijel formation, with microstructure 
evolution dependent on particle reordering at the interface, quantified using the six-fold Steinhardt order parameter \(\langle Q6 \rangle\).

@@

In Figure \ref{fig:particle_viz-field_on}, we see the effect of the
application of the magnetic field on the monolayer. The initial
configuration of particles at the monolayer show that the orientations
are random and that the particles tend to lie flat on the interface.
However, upon application of the magnetic field the particles orient to
the field direction. The effect that Gunther. et al.~observed for bijels
stabilized with anisotropic particles can also be observed in these
snapshots as the particles can be observed to have more local order in
the final state than in the initial state with no applied field. We
observe that for bijels stabilized by prolate ellipsoids, we see the
adoption of more regular arrangements of the colloids on the interface.
We investigate the effect of local particle ordering next. Past work by
Bresme and Faraudo and Davies investigating the reorientation of
particles at interfaces under magnetic fields have shown that a critical
magnetic field exists, above which the particle orients to the field and
below which the particle orientation is a function of the capillary
force and magnetic field derived force. \cite{davies_interface_2014}
\cite{bresme_orientational_2007} Particle adsorption into the interface
with microparticles have also been shown to be irreversible due to the
high adsorption energy. Upon particle reorientation, the microstructure
change can be driven solely through particle unjamming and re-jamming,
or it can be driven through the particles dragging the interface during
this process. The mechanism of unjamming and re-jamming can be
investigated using the average interfacial angle, $\langle \psi \rangle$
and the local ordering of the particles characterized with 
$\langle Q6 \rangle$ Past work has identified that local crystallization 
of colloidal crystals takes place at \(\langle Q6 \rangle = 0.38\). 
\cite{toxvaerd_role_2020}

\begin{figure} 
\centering 
\includegraphics[scale=0.3]{../figures/results/paper2/interface_angle-nint-field_on.png} 
\caption{Plots of the interface angle $(\langle \psi \rangle)$ and six fold Steinhardt order parameter 
         $(\langle Q6 \rangle)$ on the left and right respectively, versus time for bijels stabilized with 
         oblate and prolate ellipsoids on the top and bottom rows respectively. We demonstrate that upon application 
         of a magnetic field, the behavior of $(\langle \psi \rangle)$ and $(\langle Q6 \rangle)$ differ significantly 
         between oblate and prolate ellipsoids indicating that the dynamics for both particle morphologies differ. We also observe magnetic field dependence in each property for both particle types, suggesting that these changes are driven primarily through the change in the applied field strength.} 
\label{fig:interface_angle-nint-field_on} 
\end{figure}

@@

When analyzing \(\langle \psi \rangle\) for bijels stabilized by prolate
particles, this behavior can also be observed. \(\langle \psi \rangle\)
begins at \(80 ^{\circ}\). The difference in the initial
\(\langle \psi \rangle\) compared to oblate particles is due to the
direction of the axis of symmetry. In prolate particles, the axis of
symmetry lies parallel with the interface and \(\langle \psi \rangle\)
measures the angle between the interface normal and the orientation of
the axis of symmetry. We see \(\langle \psi \rangle\) decrease slightly,
before plateauing and slowly increasing again. The rate of decrease in
\(\langle \psi \rangle\) is field dependent, although given the small
decrease in \(\langle \psi \rangle\) it is unclear if the final value of
this parameter is field dependent for bijels stabilized with prolate
particles. The changes in \(\langle \psi \rangle\) for bijels stabilized
with prolate particles are small compared to bijels stabilized with
oblate particles. We believe this is due to local particle effects at
the interface. We probe this by identifying the local particle ordering
at the interface characterized by \(\langle Q6 \rangle\).

We see that for oblate particles, \(\langle Q6 \rangle\) sees a
decrease from its initial value. However the dynamics are controlled by
the applied magnetic field strength. We split the phases of dynamics
into three sections, similar to \(\langle \psi \rangle\) with the first
section seeing a decrease in \(\langle Q6 \rangle\) upon application of
the magnetic field, followed by a plateau and finally a gradual increase
before jamming takes place. These results indicate that the ordering of
the particles is reduced by the applied magnetic field, before a
restoration of some of the pre-existing order. The final values of
\(\langle Q6 \rangle\) are magnetic field dependent, with a stronger
magnetic field having a lower final \(\langle Q6 \rangle\) value
indicating that either the ordering of particles influence the angle at
the interface or vice versa. We observe that for bijels stabilized by
oblate particles, the interface ordering of the particles increases as a
function of the applied field strength. We also observe from plotting
\(\langle Q6 \rangle\) that application of a magnetic field creates a
local crystallization of the colloid monolayer characterized as
\(\langle Q6 \rangle > 0.38\). \cite{toxvaerd_role_2020}

Figure \ref{fig:domain_size-field_on}, we observed a gap between the
growth of the nematic order parameter and an increase in the domain
size. To probe why this occurs, we recast \(\langle \psi \rangle\),
\(\langle Q6 \rangle\) and \(S\) in terms of the physical phenomena
they represent. The nematic order parameter represents the ordering of
particles to an average direction, which in the case of the application
of a magnetic field, is the field direction. Therefore, a timescale
reliant on the nematic order parameter would represent a timescale of
response rate limited to the response to the magnetic field, which
indicates a particle-field orientation dependence. We name this
timescale \(\tau_S\). When applying a field to a bijel system with a
randomly oriented particle monolayer, the most significant transition
point is the isotropic to nematic transition or when \(S \geq 0.3\). We
define \(\tau_S\) for this section of the analysis by identifying when
\(S \geq 0.3\).

We can also do the same for \(\langle \psi \rangle\) and
\(\langle Q6 \rangle\). A timescale derived from
\(\langle \psi \rangle\) named \(\tau_{\langle \psi \rangle}\)
represents the capillary timescale between the interface and the
particle. Given the shape of the plot, we assign the
\(\tau_{\langle \psi \rangle}\) to be the time when the first minimum of
\(\langle \psi \rangle\) is observed for prolate particles and the first
maximum for oblate particles. A timescale derived from
\(\langle Q6 \rangle\), named \(\tau_{\langle Q6 \rangle}\) is also
calculated which represents a timescale of local particle rearrangement.
We define \(\tau_{\langle Q6 \rangle}\) as the time when
\(\langle Q6 \rangle \geq 0.38\) for prolate particles and the global
minimum of \(\tau_{\langle Q6 \rangle}\) for the oblate particles. We
omit \(\bar{B} = 0\) as previous results have identified the domain size
changes observed there. We then plot the average domain size \(L\)
against time rescaled with these three timescales in Figure
\ref{fig:domain_size-field_on-scaled}.

\begin{figure} 
\centering 
\includegraphics[scale=0.4]{../figures/results/paper2/domain_size-field_on-scaled.png} 
\caption{Plots of domain size with different timescales. The top and bottom row represent the average domain size for bijels stabilized with oblate and prolate particles respectively. The figures on the left plots the domain size against time rescaled with the nematic to isotropic transition time, $\tau_S$. The figures in the middle plot the domain size against time rescaled with the interfacial capillary timescale, $\tau_{\langle \psi \rangle}$. The figures on the right plot the domain size against time rescaled with the particle rearrangement timescale, $\tau_{\langle Q6 \rangle}$. We show that the controlling timescale when applying a magnetic field onto bijels with disordered particles is the latter timescale, indicating that the dominating effect is steric hindrance of the particles during rearrangment at the interface.} 
\label{fig:domain_size-field_on-scaled} 
\end{figure}

@@

The right plot demonstrates the domain size change after rescaling time
with \(\tau_{\langle Q6 \rangle}\) where we see good collapse between
all plots while the domain size transition also begins at
\(\frac{t}{\tau_{\langle Q6 \rangle}} = 1\). The latter point
demonstrates that the dynamics for the structural response of randomly
oriented particles are controlled by the local particle rearrangement at
the interface rather than the orientation of the particle to the
magnetic field.We see that before \(\tau_{\langle Q6 \rangle} = 1\),
\(\bar{B} = 0.2\) for the oblate particles does not collapse onto the
other plots, indicating that the dynamics before that point are
controlled by another phenomena.

@@

In Figure \ref{fig:particle_viz-field_up}, we see the effect of the
application of the magnetic field on the monolayer. The initial
configuration of particles at the monolayer show that even at initial
configuration of run \(\bar{B}: 0.2 \rightarrow 1\), most particles are
oriented towards the field. Upon increasing the field strength to
\(\bar{B} = 1\), all particles shown can be seen to be ordered to the
field, matching the results for the nematic order parameter shown in
Figure \ref{fig:domain_size-field_up}. We also observe the alignment of
the long axis of the particles to the magnetic field, demonstrating the
origin of the microstructure anisotropy. To understand how the particle
reorientation at the interface causes microstructure reorientation we
quantify the average interface angle, \(\langle \psi \rangle\) and the
local interface order of the material, \(\langle Q6 \rangle\) in Figure
\ref{fig:interface_angle-nint-field_up}.

@@

From Figure \ref{fig:interface_angle-nint-field_up}, we identify that
prolate and oblate particles respond differently at the interface. We
show that there are three time evolution trends for
\(\langle \psi \rangle\) and \(\langle Q6 \rangle\) for both oblate and
prolate particles despite the differences in the initial state of the
particles. In oblate particles \(\langle \psi \rangle\) begins closer to
\(0 ^{\circ}\) as the axis of symmetry lies close to the interface
normal. We see that for bijels experiencing a field strength history of
\(\bar{B}: 0 \rightarrow 1\) and \(\bar{B}: 0.2 \rightarrow 1\),
\(\langle \psi \rangle\) increases, plateaus and increases again before
plateauing again. This is indicative of particles tilting at the
interface, before interfacial capillary interactions ``pause'' particle
reorientation before the applied magnetic field begins to cause
particles to tilt out of the interface. We see similar trends for bijels
stabilized by prolate particles. \(\langle \psi \rangle\) begins near
\(80 ^{\circ}\). We see a decrease before reorientation ceases, and
finally \(\langle \psi \rangle\) increases again.

When looking at \(\langle Q6 \rangle\) for \(\bar{B}: 0 \rightarrow 1\)
and \(\bar{B}: 0.2 \rightarrow 1\) for oblate particles, we see that the
trends are similar with an initial decrease, followed by a plateau and
increase over time before plateauing again. \(\langle Q6 \rangle\)
generally decreases with a large decrease observed for
\(\bar{B}: 0 \rightarrow 1\) from an initial hexagonally packed system
to a structure that is locally ordered but not close packed. For prolate
particles, we see an increase in \(\langle Q6 \rangle\) with a plateau
occurring in both systems around 5000 timesteps. The significance of
this time is unknown for \(\bar{B}: 0.2 \rightarrow 1\) but for
\(\bar{B}: 1 \rightarrow 1\), this is approximately the local
crystallization point when \(\langle Q6 \rangle \geq 0.38\).

For oblate particles, we can conclude that structural response dynamics
arise from particle tilting on the interface identified as the large
difference between the initial and final \(\langle \psi \rangle\) with
an associated decrease in the interface coverage, initiating domain
coarsening. We see that this interfacial tilting causes a loss in the
close packing of oblate particles at the interface. For prolate
particles, we observe a small degree of particle tilting as can be seen
from \(\langle \psi \rangle\), although the dynamics are primarily
driven by the change in \(\langle Q6 \rangle\), indicated as a slight
dip and plateau before the particles begin reordering and packing more
tightly, decreasing the interfacial area. Larger domain size response is
observed for the prolate particles as the interfacial area change from
particle tilting at the interface is larger than that of particles close
packing at the interface.

For both particle morphologies we analyze the response of bijels with a
field history of \(\bar{B}: 0.5 \rightarrow 1\) and
\(\bar{B}: 1 \rightarrow 1\). We see a decrease in
\(\langle Q6 \rangle\) for bijels stabilized with oblate particles with
field application of \(\bar{B}: 0.5 \rightarrow 1\) compared to an
increase for \(\bar{B}: 1 \rightarrow 1\). This behavior arises from the
slight increase in the nematic order for particles in bijels
experiencing the \(\bar{B}: 0.5 \rightarrow 1\) field application
history. The \(\langle \psi \rangle\) results indicate that the
particles rearrange over time to lie flatter on the interface. For
bijels stabilized with prolate particles, we characterize a difference
in behavior between \(\bar{B}: 0.5 \rightarrow 1\) and
\(\bar{B}: 1 \rightarrow 1\). For the \(\bar{B}: 0.5 \rightarrow 1\)
case, we see a slight increase in \(\langle \psi \rangle\) before a
decrease and increase compared to the \(\bar{B}: 1 \rightarrow 1\) case
where we characterize a slight decrease over time. We also characterize
a slight decrease in \(\langle Q6 \rangle\) over time for the
\(\bar{B}: 1 \rightarrow 1\) case while characterizing a larger decrease
for the \(\bar{B}: 0.5 \rightarrow 1\) case. Similar to the oblate
particles, these results originate from the slight increase in the
nematic order for bijels experiencing the \(\bar{B}: 0.5 \rightarrow 1\)
field history.

@@

In Figure \ref{fig:domain_size_aniso-field_down}, we see that there are
small \(\Delta \bar{B}\) dependent changes in the anisotropic domain
size and tortuosity for both particle morphologies. However, there are
no clear trends that can be developed from these plots, suggesting that
the changes are overall isotropic and any differences observed arise
from the arrangement of particles. This suggests that the response of
the material to the removal of a magnetic field is isotropic and only
dependent upon the capillary interactions with the particle monolayer.
We showed earlier that the application of magnetic fields change the
local state of the particles at the interface. However the results shown
thus far demonstrate that that these changes do not seem to affect the
coarsening of the bijel once stimuli is removed. To investigate why this
is the case, we plot \(\langle \psi \rangle\) and
\(\langle Q6 \rangle\) for bijels stabilized with ellipsoidal particles
below.

@@

In Figure \ref{fig:interface_angle-field_down}, we plot
\(\langle \psi \rangle\) and \(\langle Q6 \rangle\) in the left and
right columns respectively. While there are minor differences to the
time when \(\langle \psi \rangle\) and \(\langle Q6 \rangle\) increase
and decrease respectively for bijels stabilized by oblate particles the
trends are identical. This suggests that the differences in particle
angle, local ordering and nematic order only change when coarsening will
take place without affecting its dynamics.

@@

Looking at \(\langle Q6 \rangle\), we see that all simulations see a
decrease over time. We see that contrary to previous trends, the
\(\bar{B}: 1\rightarrow 0\) simulation has a smaller change in
\(\langle Q6 \rangle\) than \(\bar{B}: 0.5\rightarrow 0\) although this
difference is also a result of the initial particle orientation and
position, rather than a defining feature of a broader trend. We see that
the \(\bar{B}: 0.5\rightarrow 0\) case is near the
\(Q6^{HCP} \approx 0.485\) boundary, suggesting it is most susceptible
to lose short range order upon removal of the magnetic field that
enforces it, resulting in the large decrease in \(\langle Q6 \rangle\)
observed.

### 2025-03-10 chapters/paper3.tex
Changes 1. Refined text in most sections 2. Resized figures for consistency of figure size 3. Removed shear banding analysis and added how shear stress is calculated

From Figure \ref{fig:stress_strain}, we show that bijels stabilized with ellipsoidal particles are shear thinning regardless of the initial 
microstructure and the processing applied. We quantify the fit and tabulate the results in Table \ref{tab:rheology_fit}. From Table 
\ref{tab:rheology_fit}, we can see that as particle order increases, signified by an increase in the initial magnetic field, the flow index 
of the material increases, indicating more Newtonian fluid like behavior. This is due to the more ordered particles being able to slip
while undergoing fluid particle interactions without affecting other particles due to orientational ordering imposed from the application 
of magnetic fields.

\begin{center}
    \begin{tabular}{||c c c c c||} 
     \hline
     Processing & $\alpha$ & $n$ & $K \frac{\Delta m (\Delta t)^{n-2}}{\Delta m} $ & $\sigma_{y} \frac{\Delta m}{\Delta m (\Delta t)^2}$ \\ [0.5ex] 
     \hline\hline
     $\bar{B}: 0 \rightarrow 0$ & 0.5 & 0.522 & 1.030 & $1.054 \cdot 10^{-4}$ \\ 
     \hline
     $\bar{B}: 0 \rightarrow 1$ & 0.5 & 0.570 & 0.975 & $5.365 \cdot 10^{-5}$ \\
     \hline
     $\bar{B}: 1 \rightarrow 0$ & 0.5 & 0.629 & 0.886 & $4.238 \cdot 10^{-5}$ \\
     \hline
     $\bar{B}: 1 \rightarrow 1$ & 0.5 & 0.637 & 0.914 & $1.714 \cdot 10^{-5}$ \\
     \hline
     $\bar{B}: 0 \rightarrow 0$ & 2 & 0.569 & 0.984 & $5.803 \cdot 10^{-5}$ \\
     \hline
     $\bar{B}: 0 \rightarrow 1$ & 2 & 0.609 & 0.944 & $4.101 \cdot 10^{-5}$ \\
     \hline
     $\bar{B}: 1 \rightarrow 0$ & 2 & 0.604 & 0.923 & $5.496 \cdot 10^{-5}$ \\
     \hline
     $\bar{B}: 1 \rightarrow 1$ & 2 & 0.618 & 0.909 & $7.161 \cdot 10^{-5}$ \\ [1ex] 
     \hline
    \end{tabular}
\label{tab:rheology_fit}
\end{center}

>>>>

From Figure \ref{fig:stress_strain}, we show that bijels stabilized with ellipsoidal particles are shear thinning regardless of the initial 
microstructure and the processing applied. We quantify the fit and tabulate the results in Table \ref{table:rheology_fit}. From Table 
\ref{table:rheology_fit}, we can see that as particle order increases, signified by an increase in the initial magnetic field, the flow index 
of the material increases, indicating more Newtonian fluid like behavior. This is due to the more ordered particles being able to slip
while undergoing fluid particle interactions without affecting other particles due to orientational ordering imposed from the application 
of magnetic fields.

\begin{table}[h!]
    \centering
    \begin{tabular}{||c c c c c||} 
     \hline
     Processing & $\alpha$ & $n$ & $K \frac{\Delta m (\Delta t)^{n-2}}{\Delta x} $ & $\sigma_{y} \frac{\Delta m}{\Delta x (\Delta t)^2}$ \\ [0.5ex] 
     \hline\hline
     $\bar{B}: 0 \rightarrow 0$ & 0.5 & 0.522 & 1.030 & $1.054 \cdot 10^{-4}$ \\ 
     \hline
     $\bar{B}: 0 \rightarrow 1$ & 0.5 & 0.570 & 0.975 & $5.365 \cdot 10^{-5}$ \\
     \hline
     $\bar{B}: 1 \rightarrow 0$ & 0.5 & 0.629 & 0.886 & $4.238 \cdot 10^{-5}$ \\
     \hline
     $\bar{B}: 1 \rightarrow 1$ & 0.5 & 0.637 & 0.914 & $1.714 \cdot 10^{-5}$ \\
     \hline
     $\bar{B}: 0 \rightarrow 0$ & 2 & 0.569 & 0.984 & $5.803 \cdot 10^{-5}$ \\
     \hline
     $\bar{B}: 0 \rightarrow 1$ & 2 & 0.609 & 0.944 & $4.101 \cdot 10^{-5}$ \\
     \hline
     $\bar{B}: 1 \rightarrow 0$ & 2 & 0.604 & 0.923 & $5.496 \cdot 10^{-5}$ \\
     \hline
     $\bar{B}: 1 \rightarrow 1$ & 2 & 0.618 & 0.909 & $7.161 \cdot 10^{-5}$ \\ [1ex] 
     \hline
    \end{tabular}
    \caption{Hershel Buckley fit parameters for different processing conditions applied to bijels stabilized by ellipsoidal particles.}
    \label{table:rheology_fit}
\end{table}

% \begin{table}[h!]
%     \centering
%     \begin{tabular}{||c c c c c c c c c c c c c||} 
%      \hline
%      $t_{sim}$ & $L_x$ & $\rho_f$ & $\tau$ & $\eta_f$ & $g_{cc'}$ & $\sigma$ & $\phi_f$ & $\rho_p$ & $\phi_p$ & $V_p$ & $d_c$ & $K_H$ \\ [0.5ex] 
%      \hline\hline
%      $10^5$ & 256 & 0.7 & 1 & 0.117 & 0.08 & 0.0267 & 0.5 & 1 & 0.15 & 2000$\pi$ & 2/3 & 100\\ [1ex] 
%      \hline
%     \end{tabular}
%     \caption{Summary of the fluid, particle and model parameters used in the proposed simulations}
%     \label{table:model_params}
%     \end{table}
